Gammapy: A Python package for gamma-ray astronomy

### 2023-01-16 src/ms-review.tex
Include comments

\gammaray data at the Data Level 3 (DL3) therefore consist in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the effective area,
point spread function (PSF) and energy dispersion.

An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
It represents the  intensity of mis-identified charged particles events that are expected
during an observation. It is defined as a function of the measured position in the field-of-view
and measured energy.

@@

In practice, the background model is subject to numerous uncertainties and needs to be corrected on the data.
Frequently, a background model is not even available and the background contribution has to be estimated
directly from the data.

@@

After all data has been projected into the same geometry, it is typically
required to improve the residual hadronic background estimate. As residual hadronic
background models can be subject to significant systematic uncertainties,
the background estimated can be improved by taking into account actual data
from regions without known \gammaray sources. This includes methods 
such as the ring or the field-of-view background techniques or
background measurements performed within, e.g. reflected regions~\citep{Berge07}.
Data measured at the field-of-view or energy boundaries of the instrument is typically
associated with a sytematic uncertainty in the IRF. For this reason this part 
of the data is often excluded from subsequent analysis by defining regions of
 "safe" data in the spatial as well as energy dimension.
All of these data reduction steps are performed by classes and functions
implemented in the \code{gammapy.makers} subpackage (see Section~\ref{ssec:gammapy-makers}).

>>>>

\gammaray data at the Data Level 3 (DL3) therefore consist of lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the effective area ($A_{\rm eff}$),
point spread function (PSF) and energy dispersion ($E_{\rm disp}$).

An additional component of DL3 IRFs is the residual hadronic background model $Bkg$.
It represents the intensity of charged particles misidentified as gamma-rays that are expected
during an observation. It is defined as a function of the measured position in the field-of-view
and measured energy.

@@

In practice, the background model is subject to numerous uncertainties and needs to be corrected on the data.
More frequently, a background model is not even available and the background contribution has to be estimated
directly from the data.

@@

After all data has been projected into the same geometry, it is typically
required to improve the residual hadronic background estimate. As residual hadronic
background models can be subject to significant systematic uncertainties,
the background estimated can be improved by taking into account actual data
from regions without known \gammaray sources. This includes methods 
such as the ring or the field-of-view background techniques or
background measurements performed within, e.g. reflected regions~\citep{Berge07}.
Data measured at the field-of-view or energy boundaries of the instrument is typically
associated with a systematic uncertainty in the IRF. For this reason this part 
of the data is often excluded from subsequent analysis by defining regions of
 "safe" data in the spatial as well as energy dimension.
All of these data reduction steps are performed by classes and functions
implemented in the \code{gammapy.makers} subpackage (see Section~\ref{ssec:gammapy-makers}).
